\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-16 public/paper/pyg4ometry.tex
better wording

\section{Conclusions and discussion}
The authors believe that tools to quickly create, either from scratch or by conversion geometry usable in Monte Carlo
particle transport programmes will save significant amounts of user effort and ultimately 
yield more accurate simulations. \PYGEOMETRY{} is a relatively complete implementation of a geometry 
creation tool, whilst heavily internally based on Geant4 and GDML, it can have utility for users of all MCRT 
codes. \PYGEOMETRY{} can clearly be extended to other formats or applications. Presently it provides a coherent and 
uniform interface to existing tools and utilities, also by using the Python programming language \PYGEOMETRY{} 
allows the programmatic control of geometry creation or modification. This approach allows the integration of 
other available tools \cite{DavisNIMA915-65} into an unified workflow.

>>>>

\section{Conclusions and discussion}
The authors believe that tools to quickly create geometry, either from scratch or by conversion,
for Monte Carlo particle transport programmes
will save significant amounts of time and user effort and will ultimately 
yield more accurate simulations. \PYGEOMETRY{} is a relatively complete implementation of a geometry 
creation tool, whilst heavily internally based on Geant4 and GDML, it can have utility for users of all MCRT 
codes. \PYGEOMETRY{} can clearly be extended to other formats or applications. Presently it provides a coherent and 
uniform interface to existing tools and utilities, also by using the Python programming language \PYGEOMETRY{} 
allows the programmatic control of geometry creation or modification. This approach allows the integration of 
other available tools \cite{DavisNIMA915-65} into an unified workflow.
